---
title: "Actividad 1 A01177261"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
```{r include=FALSE}
library(quantmod)
library(FinTS)
library(tseries)
library(rugarch)
library(openxlsx)
library(forecast)
library(tsDyn)
library("caret")
library("PerformanceAnalytics")
library("e1071")
```


```{r}
library(readxl)
library(MASS)
library(stats)
library(stats)
library(psych)
library(dplyr)
library(xlsx)

```


```{r include=FALSE}
ticker<-"^GSPC"
getSymbols(ticker,from="2020-01-01",to="2021-10-28")
```

Now, to make the lags of the price, we make a Loop For, creating the lag and storing the created lags into the xts object where the S&P500 close price is stored. 

```{r}
dji<- get("GSPC")[,4]

la<- stats::lag(dji[,1],1)
dji<- cbind(dji,la)


#Loop
for (i in 1:5)
{
  la<-stats::lag(dji[,1],i)
  dji<-cbind(dji,la)
  colnames(dji)[i+1]<-paste("Lag",i,sep="")
}

dji<-na.omit(dji)
colnames(dji)[1]<-"dji"
```


Here we make the test:
summary(lm(var dep~.,data =database))
```{r}

summary(lm(dji ~.,data =dji))

```


```{r}

atp<- ArchTest(dji [,1],lags=1)

```

If p-value is <10%, in this case is `r atp`, we conclude the presence of ARCH(1) effects.


##Primera accion: AAPL (Apple)##
```{r include=FALSE}
ticker1<-"AAPL"
getSymbols(ticker1,from="2021-01-01",to="2021-11-03")
```


```{r}
AAPL<- get("AAPL")[,4]

la<- stats::lag(AAPL[,1],1)
AAPL<- cbind(AAPL,la)


#Loop
for (i in 1:5)
{
  la<-stats::lag(AAPL[,1],i)
  AAPL<-cbind(AAPL,la)
  colnames(AAPL)[i+1]<-paste("Lag",i,sep="")
}

AAPL<-na.omit(AAPL)
colnames(AAPL)[1]<-"AAPL"
```


```{r}

summary(lm(AAPL ~.,data =AAPL))

```


```{r}

atp<- ArchTest(AAPL [,1],lags=1)

```

If p-value is <10%, in this case is `r atp`, we conclude the presence of ARCH(1) effects.


##Segunda accion: MSFT (Microsoft)##
```{r include=FALSE}
ticker2<-"MSFT"
getSymbols(ticker2,from="2021-01-01",to="2021-11-03")
```


```{r}
MSFT<- get("MSFT")[,4]

la<- stats::lag(MSFT[,1],1)
MSFT<- cbind(MSFT,la)


#Loop
for (i in 1:5)
{
  la<-stats::lag(MSFT[,1],i)
  MSFT<-cbind(MSFT,la)
  colnames(MSFT)[i+1]<-paste("Lag",i,sep="")
}

MSFT<-na.omit(MSFT)
colnames(MSFT)[1]<-"MSFT"
```


```{r}

summary(lm(MSFT ~.,data =MSFT))

```


```{r}

atp<- ArchTest(MSFT [,1],lags=1)

```

If p-value is <10%, in this case is `r atp`, we conclude the presence of ARCH(1) effects.


##Tercera accion: GOOGL (Google)##
```{r include=FALSE}
ticker3<-"GOOGL"
getSymbols(ticker3,from="2021-01-01",to="2021-11-03")
```


```{r}
GOOGL<- get("GOOGL")[,4]

la<- stats::lag(GOOGL[,1],1)
GOOGL<- cbind(GOOGL,la)


#Loop
for (i in 1:5)
{
  la<-stats::lag(GOOGL[,1],i)
  GOOGL<-cbind(GOOGL,la)
  colnames(GOOGL)[i+1]<-paste("Lag",i,sep="")
}

GOOGL<-na.omit(GOOGL)
colnames(GOOGL)[1]<-"GOOGL"
```


```{r}

summary(lm(GOOGL ~.,data =GOOGL))

```


```{r}

atp<- ArchTest(GOOGL [,1],lags=1)

```

If p-value is <10%, in this case is `r atp`, we conclude the presence of ARCH(1) effects.


##Cuarta accion: NFLX (Netflix)##
```{r include=FALSE}
ticker4<-"NFLX"
getSymbols(ticker4,from="2021-01-01",to="2021-11-03")
```


```{r}
NFLX<- get("NFLX")[,4]

la<- stats::lag(NFLX[,1],1)
NFLX<- cbind(NFLX,la)


#Loop
for (i in 1:5)
{
  la<-stats::lag(NFLX[,1],i)
  NFLX<-cbind(NFLX,la)
  colnames(NFLX)[i+1]<-paste("Lag",i,sep="")
}

NFLX<-na.omit(AAPL)
colnames(NFLX)[1]<-"NFLX"
```


```{r}

summary(lm(NFLX ~.,data =NFLX))

```


```{r}

atp<- ArchTest(NFLX [,1],lags=1)

```

If p-value is <10%, in this case is `r atp`, we conclude the presence of ARCH(1) effects.


##Quinta accion: DIS (Disney)##
```{r include=FALSE}
ticker5<-"DIS"
getSymbols(ticker5,from="2021-01-01",to="2021-11-03")
```


```{r}
DIS<- get("DIS")[,4]

la<- stats::lag(DIS[,1],1)
DIS<- cbind(DIS,la)


#Loop
for (i in 1:5)
{
  la<-stats::lag(DIS[,1],i)
  DIS<-cbind(DIS,la)
  colnames(DIS)[i+1]<-paste("Lag",i,sep="")
}

DIS<-na.omit(DIS)
colnames(DIS)[1]<-"DIS"
```


```{r}

summary(lm(DIS ~.,data =DIS))

```


```{r}

atp<- ArchTest(DIS [,1],lags=1)

```

If p-value is <10%, in this case is `r atp`, we conclude the presence of ARCH(1) effects.

